---
title: "Re_running_sensitivity_post_PF"
author: "Tess McCabe"
date: "4/1/2022"
output: html_document
---


After running a particle filter on the knots from Istem's emulator, Mike and I want to do a final test that shows that our constraint actually leads to matching the data better. Istem actually already set up a similar functionality in the PDA code. I am basing my re-run off of three things:
- The script she alreayd wrote, documented here: https://pecanproject.github.io/pecan-documentation/develop/othervignettes.html#post-pda-analyses
- The combined prior of the meta-analysis + the PF, found here: /fs/data2/output//PEcAn_PDA_for_PF/pft/cogongrass2/PDA_MA_post.Rdata
- A functionality that Istem described in this part of the vignette: https://github.com/PecanProject/pecan/blob/develop/modules/assim.batch/vignettes/AssimBatchVignette.Rmd#L110, that you can pass a posterior object instead of a posterior ID to the xml. 

```{r}

source("~/pecan/modules/uncertainty/R/get.parameter.samples.R")
source("~/pecan/base/workflow/R/run.write.configs.R")
source("~/pecan/modules/uncertainty/R/ensemble.R")
 source("~/pecan/base/workflow/R/start_model_runs.R")
source("~/pecan/models/ed/R/model2netcdf.ED2.R")
source("~/pecan/modules/assim.batch/R/pda.generate.externals.R")
source("~/pecan/base/utils/R/read.output.custom.R")
source("~/pecan/modules/benchmark/R/align_data.R")
source("~/pecan/models/ed/R/write.configs.ed.R")
source("~/pecan/modules/assim.batch/R/pda.get.model.output.R")
source("~/pecan/modules/assim.batch/R/pda.define.llik.R")
# read post-PDA settings if you don't have them in your wotking environment
 #replace the *** with the ensemble id given by the workflow
# postPDA.settings <- read.settings("/fs/data2/output//PEcAn_PDA_for_PF/pecan.pdaPDA_for_PF_post_path.xml") ## PDA settings where I swapped the posterior PFT posterior id with the path to the combined prior
# 
# 
#  # Call model specific write.configs
  # postPDA.settings <- run.write.configs(settings = postPDA.settings,
  #                         write= FALSE,
  #                         ens.sample.method= postPDA.settings$ensemble$samplingspace$parameters$method,
  #                         posterior.files = "/fs/data2/output//PEcAn_PDA_for_PF/pft/cogongrass2/PDA_MA_post.Rdata",
  #                         prioritize_prior = TRUE)
# 
#  # Let's save the settings with the new ensemble id
#  PEcAn.settings::write.settings(postPDA.settings, outputfile=paste0('pecan.pda.redo.sensitivity', postPDA.settings$assim.batch$ensemble.id,'.xml'))
# 
 postPDA.settings <- read.settings("/fs/data2/output//PEcAn_PDA_for_PF/pecan.pda.redo.sensitivityPDA_for_PF.xml")
# 
#  #### Start ecosystem model runs, this one takes awhile...
#  start_model_runs(postPDA.settings, FALSE) ## Hacky Took from github when I probably should do a pull. 
 
#  outfile <- postPDA.settings$host$outdir
#  run_ids <- list.files(outfile, pattern = "ENS*")
# 
# pfts <- list()
# pfts$pft$name <- "cogongrass2"
# 
# 
# for(i in seq_along(run_ids)){
# 
#   if(i > 5){ # PFT write-out error at /projectnb/dietzelab/pecan.data/output//tmccabe/PDA_for_PF/out/ENS-00005-1000026928//2017.nc is format NC_FORMAT_NETCDF4
#     file_path <- paste(outfile,"/", run_ids[i],"/", sep = "")
#   system(paste0("mkdir ", file_path, "t_files"))
#   system(paste0("mv ", file_path, "*-T-* ", file_path, "t_files"))
#   model2netcdf.ED2(file_path,
#                    postPDA.settings$run$site$lat,
#                    postPDA.settings$run$site$lon,
#                    start_date = postPDA.settings$run$start.date,
#                    end_date = postPDA.settings$run$end.date, pfts = pfts)
#   }
# 
# 
# }

 # Get results of model runs
postPDA.settings$modeloutdir <- postPDA.settings$host$outdir

  get.results(postPDA.settings)

 # Repeat ensemble analysis with PDA-constrained params
 run.ensemble.analysis(postPDA.settings, variable = "AbvGrndWood")
 
## Let's run the sudo cogongrass outputs
 
 
#  outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020054/out/" ## LAI, 50 ensemble suddocogon. 70 ids though. Why??????
#  run_ids <- list.files(outfile)
# 
#  pfts <- list()
#  pfts$pft$name <- "sudoCogongrass2"
# 
# for(i in seq_along(run_ids)){
# 
# if (i > 70){
#     file_path <- paste(outfile,"/", run_ids[i],"/", sep = "")
#   system(paste0("mkdir ", file_path, "t_files"))
#   system(paste0("mv ", file_path, "*-T-* ", file_path, "t_files"))
#   model2netcdf.ED2(file_path,
#                    postPDA.settings$run$site$lat,
#                    postPDA.settings$run$site$lon,
#                    start_date = postPDA.settings$run$start.date,
#                    end_date = postPDA.settings$run$end.date, pfts = pfts)
# 
# }
#   
# 
# 
# }

 
 outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020054/out/" ## LAI, 50 ensemble suddocogon. 70 ids though. Why??????
 run_ids <- list.files(outfile)

 pfts <- list()
 pfts$pft$name <- "sudoCogongrass2"

for(i in seq_along(run_ids)){

if(i > 31){
  file_path <- paste(outfile,"/", run_ids[i],"/","t_files", "/", sep = "")
 
  model2netcdf.ED2(file_path,
                   postPDA.settings$run$site$lat,
                   postPDA.settings$run$site$lon,
                   start_date = postPDA.settings$run$start.date,
                   end_date = postPDA.settings$run$end.date, pfts = pfts)
  
}
    



}
 
## Load sugocogognrass into new biomass object sudobiomass <-----------
  outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020054/out/" 
  id <- "1000020054"
  knots <- list.files(path = outfile, pattern = "1003")
  sudoBiomass <- tibble(abg = rep(NA, length(knots)), bgb = rep(NA, length(knots)), lai = rep(NA, length(knots)))
  bad_runs <- c("1003213881", "1003213887", "1003213888")
  for(i in seq_along(knots)){
    path <- paste0("/projectnb/dietzelab/pecan.data/output//tmccabe/", id, "/out/", knots[i], "/")

    if(knots[i] %in% bad_runs){
      next
    }
        status <- read.delim(paste0(path, "README.txt"), sep = ":", header = FALSE)
    sensitivity <- grep("sensitivity analysis", x = status$V2[1])
    
    if(rlang::is_empty(sensitivity)){
      nc <- try(ncdf4::nc_open(paste0(path, "2019.nc")))
    if(class(nc) != "try-error"){
      agb <- ncdf4::ncvar_get(nc, "AbvGrndWood")
      bgb <- ncdf4::ncvar_get(nc, "TotSoilCarb")

      sudoBiomass$abg[i] <- agb[4] ## Take most recent value
      sudoBiomass$bgb[i] <- bgb[4]
      ncdf4::nc_close(nc)
    }else{
      next
    }
    }
  
    
    rm(nc)
  }
 

 # ## let's re-load the pre-PDA ensemble outputs

#  outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020051/out/"
#  run_ids <- list.files(outfile)
# 
#  pfts <- list()
#  pfts$pft$name <- "cogongrass2"
# 
# for(i in seq_along(run_ids)){
# 
# 
#     file_path <- paste(outfile,"/", run_ids[i],"/", sep = "")
#   system(paste0("mkdir ", file_path, "t_files"))
#   system(paste0("mv ", file_path, "*-T-* ", file_path, "t_files"))
#   model2netcdf.ED2(file_path,
#                    postPDA.settings$run$site$lat,
#                    postPDA.settings$run$site$lon,
#                    start_date = postPDA.settings$run$start.date,
#                    end_date = postPDA.settings$run$end.date, pfts = pfts)
# 
# 
# 
# }

 outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020051/out/"
 run_ids <- list.files(outfile)

 pfts <- list()
 pfts$pft$name <- "cogongrass2"

for(i in seq_along(run_ids)){


    file_path <- paste(outfile,"/", run_ids[i],"/","t_files", "/", sep = "")
 
  model2netcdf.ED2(file_path,
                   postPDA.settings$run$site$lat,
                   postPDA.settings$run$site$lon,
                   start_date = postPDA.settings$run$start.date,
                   end_date = postPDA.settings$run$end.date, pfts = pfts)



}
 pre_pda_sensitivity_path <- list.files("/projectnb/dietzelab/pecan.data/output//tmccabe/1000020051/out", pattern = "1003") ## Sensitivity trait was LAI
 
 
  outfile <- "/projectnb/dietzelab/pecan.data/output//tmccabe/1000020051/out"
  id <- "1000020051"
  knots <- list.files(path = outfile)
  biomass <- tibble(abg = rep(NA, length(knots)), bgb = rep(NA, length(knots)), lai = rep(NA, length(knots)))
  bad_runs <- c()
  for(i in seq_along(knots)){
    path <- paste0("/projectnb/dietzelab/pecan.data/output//tmccabe/", id, "/out/", knots[i], "/")

    if(knots[i] %in% bad_runs){
      next
    }
    status <- read.delim(paste0(path, "README.txt"), sep = ":", header = FALSE)
    sensitivity <- grep("sensitivity analysis", x = status$V2[1])
    
    if(rlang::is_empty(sensitivity)){
       nc <- try(ncdf4::nc_open(paste0(path, "2019.nc")))
    if(class(nc) != "try-error"){
      agb <- ncdf4::ncvar_get(nc, "AbvGrndWood")
      bgb <- ncdf4::ncvar_get(nc, "TotSoilCarb")

      biomass$abg[i] <- agb[4] ## Take most recent value
      biomass$bgb[i] <- bgb[4]
      ncdf4::nc_close(nc)
    }else{
      next
    }
      
    }
   
    rm(nc)
  }
 
 # pre_pda_sensitivity_path <- list.files("/fs/data2/output//PEcAn_1000019795/out/", pattern = "1003188") ## Sensitivity trait was SLA
 # 
 #  outfile <- "/fs/data2/output//PEcAn_1000019795/out/"
 #  id <- "1000019795"
 #  knots <- list.files(path = outfile, pattern = "1003188")
 #  biomass <- tibble(abg = rep(NA, length(knots)), bgb = rep(NA, length(knots)), lai = rep(NA, length(knots)))
 #  bad_runs <- c("1003188425")
 #  for(i in seq_along(knots)){
 #    path <- paste0("/fs/data2/output//PEcAn_", id, "/out/", knots[i], "/")
 # 
 #    if(knots[i] %in% bad_runs){
 #      next
 #    }
 # 
 #    nc <- try(ncdf4::nc_open(paste0(path, "2019.nc")))
 #    if(class(nc) != "try-error"){
 #      agb <- ncdf4::ncvar_get(nc, "AbvGrndWood")
 #      bgb <- ncdf4::ncvar_get(nc, "TotSoilCarb")
 # 
 #      biomass$abg[i] <- agb[4] ## Take most recent value
 #      biomass$bgb[i] <- bgb[4]
 #      ncdf4::nc_close(nc)
 #    }else{
 #      next
 #    }
 #    #rm(nc)
 #  }


# outfile <- "/fs/data2/output//PEcAn_PDA_for_PF/out/"
# 
# id <- "PDA_for_PF"
# name <-"PDA_for_PF" #"PDA_50kn_MODEL_REDO_after_fix_of_obs"#"50_knots_local"
# 
# knots <- list.files(path = outfile, pattern = "knot")
# 
# biomass <- tibble(abg = rep(NA, length(knots)), bgb = rep(NA, length(knots)))
# 
# #bad_runs <- c(26)
# #bad_runs <- c(47)
# bad_runs <- c()
# 
# for(i in seq_along(knots)){
#   path <- paste0("/fs/data2/output//PEcAn_", id, "/out/", name, ".knot.", i, "/")
# 
#   if(i %in% bad_runs){
#     next
#   }
# 
#   nc <- try(ncdf4::nc_open(paste0(path, "2019.nc")))
#   if(class(nc) != "try-error"){
#     agb <- ncdf4::ncvar_get(nc, "AbvGrndWood")
#     bgb <- ncdf4::ncvar_get(nc, "TotSoilCarb")
# 
#     biomass$abg[i] <- agb[4] ## Take most recent value
#     biomass$bgb[i] <- bgb[4]
#     ncdf4::nc_close(nc)
#   }else{
#     next
#   }
#   rm(nc)
# }





 
 
 # nowload the post-PDA ensemble outputs

  outfile <- postPDA.settings$host$outdir
  knots <- list.files(path = outfile, pattern = "ENS-000")
  biomass_post_pda  <- tibble(abg = rep(NA, length(knots)), bgb = rep(NA, length(knots)))
  bad_runs <- c("ENS-00005-1000026928")
  for(i in seq_along(knots)){
    path <- paste0(outfile, "/", knots[i], "/")

    if(knots[i] %in% bad_runs){
      next
    }

    nc <- try(ncdf4::nc_open(paste0(path, "2019.nc")))
    if(class(nc) != "try-error"){
      agb <- ncdf4::ncvar_get(nc, "AbvGrndWood")
      bgb <- ncdf4::ncvar_get(nc, "TotSoilCarb")

      biomass_post_pda$abg[i] <- agb[4] ## Take most recent value
      biomass_post_pda$bgb[i] <- bgb[4]
      ncdf4::nc_close(nc)
    }else{
      next
    }
    #rm(nc)
  }
  

  
 ## Load observations
biomass_obs <- read.csv("~/fs_ed/SERDP_Project/Cogongrass_trait_sampling/allometries/Cogongrass_Biomass_datasheet_2019.csv") ## Data in g biomass_obs

biomass_obs$Quadrat.area <- 30^2 # 30 cm^2
biomass_obs$fine_roots_corrected_area <- biomass_obs$dry.biomass.fine.root.g / biomass_obs$Soil.Core.cross.sectional.area.cm.2
biomass_obs$rhizome_corrected_area <- biomass_obs$dry.biomass.rhizome/ biomass_obs$Soil.Core.cross.sectional.area.cm.2
biomass_obs$leaves_corrected <- biomass_obs$Dry.biomas.leaves.g/ biomass_obs$Quadrat.area
biomass_obs$tillars_corrected <- biomass_obs$dry.biomass.tiller/ biomass_obs$Quadrat.area

drought <- dplyr::filter(biomass_obs, biomass_obs$Treatment == "Drought") 
ambient <- dplyr::filter(biomass_obs, biomass_obs$Treatment == "Ambient")
g_to_kg <- 1000
cm2_to_m2 <- 10000
biomass_to_c <- 0.5

ambient$fine_roots_corrected_area <- (ambient$fine_roots_corrected_area/g_to_kg ) * cm2_to_m2 * biomass_to_c ## 1000 g -> kg 10000 cm^2 -> m^2 0.5 Kg Biomass -> Kg C
ambient$tillars_corrected <- (ambient$tillars_corrected/g_to_kg ) * cm2_to_m2 * biomass_to_c
ambient$leaves_corrected <- (ambient$leaves_corrected/g_to_kg ) * cm2_to_m2 * biomass_to_c
ambient$rhizome_corrected_area <- (ambient$rhizome_corrected_area/g_to_kg ) * cm2_to_m2 * biomass_to_c

ambient$agb <- ambient$tillars_corrected + ambient$leaves_corrected
ambient$bgb <- ambient$fine_roots_corrected_area + ambient$rhizome_corrected_area

drought$fine_roots_corrected_area <- (drought$fine_roots_corrected_area/g_to_kg ) * cm2_to_m2 * biomass_to_c ## 1000 g -> kg 10000 cm^2 -> m^2 0.5 Kg Biomass -> Kg C
drought$tillars_corrected <- (drought$tillars_corrected/g_to_kg ) * cm2_to_m2 * biomass_to_c
drought$leaves_corrected <- (drought$leaves_corrected/g_to_kg ) * cm2_to_m2 * biomass_to_c
drought$rhizome_corrected_area <- (drought$rhizome_corrected_area/g_to_kg ) * cm2_to_m2 * biomass_to_c

drought$agb <- drought$tillars_corrected + drought$leaves_corrected
drought$bgb <- drought$fine_roots_corrected_area + drought$rhizome_corrected_area


```


## Plot comparisons
```{r}
  
 ## plot comparisons
plot(ambient$agb, ambient$bgb, ylab = "belowground biomass", xlab = "aboveground biomass", main = "Below & aboveground", pch = 4)
points(biomass$abg, biomass$bgb, col = "#2CBEC5")
points(biomass_post_pda$abg, biomass_post_pda$bgb, col = "#7570b3")
legend("topleft", 
  legend = c("Observations","Post-constraint", "Pre-constraint"), 
  fill = c("black", "#7570b3", "#2CBEC5"))

## Look at below ground and aboveboard separately 

# Because there are a different number of model runs than observations, putting model runs into bins based on number of observations
rescale <- function(scale, vec, quant = seq(0, 1, length.out = length(scale))){
  rank <- cut(vec, breaks = quantile(scale,  quant, na.rm = TRUE)) # Transform the numeric variable in bins
  rank <- as.factor(as.numeric(rank))
  levels(rank) <- as.character(round(quant * 100))
  return(rank)
}

ambient$agb_rank <- rescale(ambient$agb, ambient$agb)
biomass$abg_rank <- rescale(ambient$agb, biomass$abg)
biomass_post_pda$agb_rank <- rescale(ambient$agb, biomass_post_pda$abg)

ambient$bgb_rank <- rescale(ambient$bgb, ambient$bgb)
biomass$bgb_rank <- rescale(ambient$bgb, biomass$bgb)
biomass_post_pda$bgb_rank <- rescale(ambient$bgb, biomass_post_pda$bgb)


plot(y = ambient$agb, x = ambient$agb_rank, ylab = "Aboveground biomass", xlab = "Quantile rank", ylim = c(0.025, 0.3), main = "Aboveground Biomass")
points(y = biomass$abg, x = jitter(as.numeric(biomass$abg_rank)), col = "#2CBEC5")
points(y = biomass_post_pda$abg, x = biomass_post_pda$agb_rank, col = "#7570b3")
legend("topleft", 
  legend = c("Observations","Post-constraint", "Pre-constraint"), 
  fill = c("black", "#7570b3", "#2CBEC5"))

plot(y = ambient$bgb, x = ambient$bgb_rank, ylab = "Belowground biomass", xlab = "Quantile rank", main = "Belowground Biomass")
points(y = biomass$bgb, x = jitter(as.numeric(biomass$bgb_rank)), col = "#2CBEC5")
points(y = biomass_post_pda$bgb, x = biomass_post_pda$bgb_rank, col = "#7570b3")
legend("topleft", 
  legend = c("Observations","Post-constraint", "Pre-constraint"), 
  fill = c("black", "#7570b3", "#2CBEC5"))


line_w <- 3
plot(density(ambient$agb), ylim = c(0, 35), main = "Aboveground Biomass:  Before and After PDA", xlab = "Aboveground biomass", xlim = c(0, 0.35), col = "dark red",  lwd = line_w)
lines(density(na.omit(biomass$abg)), col = "#2CBEC5" ,  lwd = line_w)
lines(density(na.omit(biomass_post_pda$abg)), col = "#7570b3" ,  lwd = line_w)
legend("topleft", 
  legend =  c("Observations","Post-Feild Work", "Pre-PDA"), 
  fill = c("dark red", "#7570b3", "#2CBEC5"))

plot(density(na.omit(ambient$bgb)), main = "Belowground Biomass: Before and After PDA", xlab = "Belowground biomass", ylim = c(0,8), xlim = c(0, 0.85), col = "dark red", lwd = line_w)
lines(density(na.omit(biomass$bgb)), col = "#2CBEC5",  lwd = line_w )
lines(density(na.omit(biomass_post_pda$bgb)), col = "#7570b3",  lwd = line_w )
legend("topleft", 
  legend = c("Observations","Post-Feild Work", "Pre-PDA"), 
  fill = c("dark red", "#7570b3", "#2CBEC5"))

### WITH THE PRIORS ONLY RUNS TOO


plot(density(ambient$agb), ylim = c(0, 50), main = "Aboveground Biomass: Pre-constraint from pre-made sensitivity analysis", xlab = "Aboveground biomass")
lines(density(na.omit(sudoBiomass$abg)), col = "#F47769")
lines(density(na.omit(biomass$abg)), col = "#2CBEC5" )
lines(density(na.omit(biomass_post_pda$abg)), col = "#7570b3" )
legend("topleft", 
  legend = c("Observations", "Priors Only","Field + PDA", "Field"), 
  fill = c("black","#F47769", "#7570b3", "#2CBEC5"))

plot(density(na.omit(ambient$bgb)), main = "Belowground Biomass: Pre-constraint from pre-made sensitivity analysis", xlab = "Belowground biomass", ylim = c(0,8), xlim = c(0, 1.2))
lines(density(na.omit(sudoBiomass$bgb)), col = "#F47769")
lines(density(na.omit(biomass$bgb)), col = "#2CBEC5" )
lines(density(na.omit(biomass_post_pda$bgb)), col = "#7570b3" )
legend("topleft", 
  legend = c("Observations", "Priors Only","Field + PDA", "Field"), 
  fill = c("black","#F47769", "#7570b3", "#2CBEC5"))


######## SEEING IF DROUGHT DIFFERENT

plot(density(ambient$agb), ylim = c(0, 40), main = "Aboveground Biomass: Pre-constraint from pre-made sensitivity analysis", xlab = "Aboveground biomass")
lines(density(na.omit(sudoBiomass$abg)), col = "#F47769")
lines(density(na.omit(drought$agb)), col = "red")
lines(density(na.omit(biomass$abg)), col = "#2CBEC5" )
lines(density(na.omit(biomass_post_pda$abg)), col = "#7570b3" )
legend("topleft", 
  legend = c("Observations","dorught obs","Priors Only", "Post-constraint", "Pre-constraint"), 
  fill = c("black", "red", "#F47769", "#7570b3", "#2CBEC5"))

plot(density(na.omit(ambient$bgb)), main = "Belowground Biomass: Pre-constraint from pre-made sensitivity analysis", xlab = "Belowground biomass", ylim = c(0,12))
lines(density(na.omit(drought$bgb)), col = "red")
lines(density(na.omit(biomass$bgb)), col = "#2CBEC5" )
lines(density(na.omit(sudoBiomass$bgb)), col = "#F47769")
lines(density(na.omit(biomass_post_pda$bgb)), col = "#7570b3" )
legend("topleft", 
  legend = c("Observations","dorught obs","Priors Only", "Post-constraint", "Pre-constraint"), 
  fill = c("black", "red", "#F47769", "#7570b3", "#2CBEC5"))


plot(ambient$agb, ambient$bgb, ylab = "belowground biomass", xlab = "aboveground biomass", main = "Below & aboveground", pch = 4)
points(sudoBiomass$abg, sudoBiomass$bgb, col = "#F47769")
points(drought$agb, drought$bgb, col = "red")
points(biomass$abg, biomass$bgb, col = "#2CBEC5")
points(biomass_post_pda$abg, biomass_post_pda$bgb, col = "#7570b3")
legend("topleft", 
  legend = c("Observations","dorught obs", "Post-constraint", "Pre-constraint"), 
  fill = c("black", "red","#F47769", "#7570b3", "#2CBEC5"))

# plot(sort(ambient$bgb))
# points(sort(biomass$bgb), col = "#2CBEC5")
# points(sort(biomass_post_pda$bgb), col = "#7570b3")
# legend("topleft", 
#   legend = c("Observations","Post-constraint", "Pre-constraint"), 
#   fill = c("black", "#7570b3", "#2CBEC5"))
 # save the comparison plots to pdf

### Check if the ratios are different




```


## Re-run sensitivity analysis
```{r}

 # Repeat variance decomposition to see how constraints have changed
 #run.sensitivity.analysis()
 #postPDA.settings$ensemble$ensemble.id <- "NOENSEMBLEID"
 postPDA.settings$sensitivity.analysis$ensemble.id <- "NOENSEMBLEID"
 run.sensitivity.analysis(postPDA.settings, variable = "LAI")
 
```